Models

### 2024-03-12 analysis/05_model_metrics.Rmd
add protected area models

      group_slopes <- as_tibble(slopes$emtrends) %>%
        mutate(effect = "group_slope", group = model_id) %>%
        rename(std.error = SE, estimate = year_scaled.trend, term = model_id)

@@

raw_value_mods <- tibble(metric_name = raw_metrics, 
                         base = "value ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "value ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "value ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "value ~ year_scaled * climate + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula") %>%
  #don't fit the CWM_litter_size_min_n and climate model, not enough data
  filter(metric_name != "CWM_litter_size_min_n" | model_id != "climate")

log_mods <- tibble(metric_name = log_metrics, 
                         base = "log(value) ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "log(value) ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "log(value) ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "log(value) ~ year_scaled * climate + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

logone_mods <- tibble(metric_name = logone_metrics, 
                         base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "logvalue ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "logvalue ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "logvalue ~ year_scaled * climate + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

>>>>

      group_slopes <- as_tibble(slopes$emtrends) %>%
        mutate(effect = "group_slope", group = model_id) %>%
        rename(std.error = SE, estimate = year_scaled.trend, term = model_id) %>%
        mutate(term = as.character(term))

@@

raw_value_mods <- tibble(metric_name = raw_metrics, 
                         base = "value ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "value ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "value ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "value ~ year_scaled * climate + (year_scaled|study_id/rarefyID)",
                         protected_area = "value ~ year_scaled * protected_area + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate, protected_area), names_to = "model_id", values_to = "formula") %>%
  #don't fit the CWM_litter_size_min_n and climate model, not enough data
  filter(metric_name != "CWM_litter_size_min_n" | model_id != "climate")

log_mods <- tibble(metric_name = log_metrics, 
                         base = "log(value) ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "log(value) ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "log(value) ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "log(value) ~ year_scaled * climate + (year_scaled|study_id/rarefyID)",
                   protected_area = "value ~ year_scaled * protected_area + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate, protected_area), names_to = "model_id", values_to = "formula")

logone_mods <- tibble(metric_name = logone_metrics, 
                         base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "logvalue ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "logvalue ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "logvalue ~ year_scaled * climate + (year_scaled|study_id/rarefyID)",
                      protected_area = "value ~ year_scaled * protected_area + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate, protected_area), names_to = "model_id", values_to = "formula")
